\artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-21 Core/doc/latex/paper.tex
adjustments: KIT colors, numbers from Joram's thesis'

\begin{figure}[p]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics.
I/O intensive operations are done in highly parallel in the WLCG.
The computing-intensive operations are only performed if really necessary.
This means that selection steps are performed as early as possible.}
\label{figure_analysis_steps}
\end{figure}
\todo{Should we drop CMS-specific technical terms like AOD/miniAOD?
Maybe not put this figure on a dedicated page?}
\clearpage

>>>>

\begin{figure}[p]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics, numbers taken from \cite{joram_phd}. Data size is reduced by six orders of magnitude, turnaround time by 4. I/O intensive operations are done in highly parallel in the WLCG.
The computing-intensive operations are only performed if really necessary.
This means that selection steps are performed as early as possible.}
\label{figure_analysis_steps}
\end{figure}
\todo{Should we drop CMS-specific technical terms like AOD/miniAOD?
Maybe not put this figure on a dedicated page?}
\clearpage
